### 2024-08-09 NN/tables/backward.tex
zz

    \begin{table*}
        \centering
        \begin{tabular}{lr}
\hline
 features                                                                                                     &    R2 \\
\hline
 flow\_rate1, conc\_nano1, Kfluid1, heat\_flux1, X\_D1, flow\_rate2, conc\_nano2, Kfluid2, heat\_flux2, X\_D2 & 82.69 \\
 conc\_nano1, Kfluid1, heat\_flux1, X\_D1, flow\_rate2, conc\_nano2, Kfluid2, heat\_flux2, X\_D2              & 62.45 \\
 flow\_rate1, Kfluid1, heat\_flux1, X\_D1, flow\_rate2, conc\_nano2, Kfluid2, heat\_flux2, X\_D2              & 81.63 \\
 flow\_rate1, conc\_nano1, heat\_flux1, X\_D1, flow\_rate2, conc\_nano2, Kfluid2, heat\_flux2, X\_D2          & 73.64 \\
 flow\_rate1, conc\_nano1, Kfluid1, X\_D1, flow\_rate2, conc\_nano2, Kfluid2, heat\_flux2, X\_D2              & 72.94 \\
 flow\_rate1, conc\_nano1, Kfluid1, heat\_flux1, flow\_rate2, conc\_nano2, Kfluid2, heat\_flux2, X\_D2        & 67.45 \\
 flow\_rate1, conc\_nano1, Kfluid1, heat\_flux1, X\_D1, conc\_nano2, Kfluid2, heat\_flux2, X\_D2              & 68.03 \\
 flow\_rate1, conc\_nano1, Kfluid1, heat\_flux1, X\_D1, flow\_rate2, Kfluid2, heat\_flux2, X\_D2              & 76.57 \\
 flow\_rate1, conc\_nano1, Kfluid1, heat\_flux1, X\_D1, flow\_rate2, conc\_nano2, heat\_flux2, X\_D2          & 38.28 \\
 flow\_rate1, conc\_nano1, Kfluid1, heat\_flux1, X\_D1, flow\_rate2, conc\_nano2, Kfluid2, X\_D2              & 69.39 \\
 flow\_rate1, conc\_nano1, Kfluid1, heat\_flux1, X\_D1, flow\_rate2, conc\_nano2, Kfluid2, heat\_flux2        & 81.61 \\
\hline
\end{tabular}
        \caption{Results of Backward Feature Elimination}
        \label{backward}
    \end{table*}

>>>>

    \begin{table*}[h]
        \centering
        \begin{tabular}{lr}
\hline
 features                                                                                                                                 &    R2 \\
\hline
 SG Coating, Temp Alk Sol, NaOH Wt\%, Dip Time Alk (min), pH Sol, Hydro Time (h), Dip Time Sol (s), Clay Conc, Cure Time (min), Cure Temp & 89.74 \\
 Temp Alk Sol, NaOH Wt\%, Dip Time Alk (min), pH Sol, Hydro Time (h), Dip Time Sol (s), Clay Conc, Cure Time (min), Cure Temp             & 66.46 \\
 SG Coating, NaOH Wt\%, Dip Time Alk (min), pH Sol, Hydro Time (h), Dip Time Sol (s), Clay Conc, Cure Time (min), Cure Temp               & 66.46 \\
 SG Coating, Temp Alk Sol, Dip Time Alk (min), pH Sol, Hydro Time (h), Dip Time Sol (s), Clay Conc, Cure Time (min), Cure Temp            & 66.46 \\
 SG Coating, Temp Alk Sol, NaOH Wt\%, pH Sol, Hydro Time (h), Dip Time Sol (s), Clay Conc, Cure Time (min), Cure Temp                     & 89.54 \\
 SG Coating, Temp Alk Sol, NaOH Wt\%, Dip Time Alk (min), Hydro Time (h), Dip Time Sol (s), Clay Conc, Cure Time (min), Cure Temp         &  9.16 \\
 SG Coating, Temp Alk Sol, NaOH Wt\%, Dip Time Alk (min), pH Sol, Dip Time Sol (s), Clay Conc, Cure Time (min), Cure Temp                 & 87.32 \\
 SG Coating, Temp Alk Sol, NaOH Wt\%, Dip Time Alk (min), pH Sol, Hydro Time (h), Clay Conc, Cure Time (min), Cure Temp                   & 63.66 \\
 SG Coating, Temp Alk Sol, NaOH Wt\%, Dip Time Alk (min), pH Sol, Hydro Time (h), Dip Time Sol (s), Cure Time (min), Cure Temp            & 44.54 \\
 SG Coating, Temp Alk Sol, NaOH Wt\%, Dip Time Alk (min), pH Sol, Hydro Time (h), Dip Time Sol (s), Clay Conc, Cure Temp                  & 56.51 \\
 SG Coating, Temp Alk Sol, NaOH Wt\%, Dip Time Alk (min), pH Sol, Hydro Time (h), Dip Time Sol (s), Clay Conc, Cure Time (min)            & 66.27 \\
\hline
\end{tabular}
        \caption{Results of Backward Feature Elimination}
        \label{backward}
    \end{table*}

### 2024-08-09 NN/tables/forward.tex
zz

    \begin{table*}[h]
        \centering
        \begin{tabular}{lr}
\hline
 features                                                         &     R2 \\
\hline
 pH Sol                                                           &  14.56 \\
 Hydro Time (h)                                                   &  26.4  \\
 Dip Time Sol (s)                                                 &  11.24 \\
 Clay Conc                                                        &  64.24 \\
 Cure Time (min)                                                  &   0.1  \\
 SG Coating, Clay Conc                                            &  64.93 \\
 Temp Alk Sol, Clay Conc                                          &  64.93 \\
 NaOH Wt\%, Clay Conc                                             &  64.93 \\
 Dip Time Alk (min), Clay Conc                                    &  79.07 \\
 pH Sol, Clay Conc                                                &  62.87 \\
 Hydro Time (h), Clay Conc                                        & -15.61 \\
 Dip Time Sol (s), Clay Conc                                      &  80.99 \\
 Cure Time (min), Clay Conc                                       &  74.1  \\
 Cure Temp, Clay Conc                                             &  66.68 \\
 SG Coating, Clay Conc, Dip Time Sol (s)                          &  81.03 \\
 Temp Alk Sol, Clay Conc, Dip Time Sol (s)                        &  81.03 \\
 NaOH Wt\%, Clay Conc, Dip Time Sol (s)                           &  81.03 \\
 Dip Time Alk (min), Clay Conc, Dip Time Sol (s)                  &  93.94 \\
 pH Sol, Clay Conc, Dip Time Sol (s)                              &  83.22 \\
 Hydro Time (h), Clay Conc, Dip Time Sol (s)                      &  56.92 \\
 Cure Time (min), Clay Conc, Dip Time Sol (s)                     &  60.09 \\
 Cure Temp, Clay Conc, Dip Time Sol (s)                           &  60.67 \\
 SG Coating, Clay Conc, Dip Time Sol (s), Dip Time Alk (min)      &  85.55 \\
 Temp Alk Sol, Clay Conc, Dip Time Sol (s), Dip Time Alk (min)    &  85.55 \\
 NaOH Wt\%, Clay Conc, Dip Time Sol (s), Dip Time Alk (min)       &  85.55 \\
 pH Sol, Clay Conc, Dip Time Sol (s), Dip Time Alk (min)          &  77.04 \\
 Hydro Time (h), Clay Conc, Dip Time Sol (s), Dip Time Alk (min)  &  75.85 \\
 Cure Time (min), Clay Conc, Dip Time Sol (s), Dip Time Alk (min) &  71.81 \\
 Cure Temp, Clay Conc, Dip Time Sol (s), Dip Time Alk (min)       &  63.33 \\
\hline
\end{tabular}
        \caption{Results of Forward Feature Selection for different features}
        \label{forward}
    \end{table*}

>>>>

    \begin{table*}[h]
        \centering
        \begin{tabular}{lr}
\hline
 features                                                            &     R2 \\
\hline
 pH Sol                                                              &  14.96 \\
 Hydro Time (h)                                                      &  33.65 \\
 Dip Time Sol (s)                                                    &  11.2  \\
 Clay Conc                                                           &  68.7  \\
 Cure Time (min)                                                     & -15.76 \\
 SG Coating, Clay Conc                                               &  63.12 \\
 Temp Alk Sol, Clay Conc                                             &  63.12 \\
 NaOH Wt\%, Clay Conc                                                &  63.12 \\
 Dip Time Alk (min), Clay Conc                                       &  47.64 \\
 pH Sol, Clay Conc                                                   &  77.65 \\
 Hydro Time (h), Clay Conc                                           & -24.51 \\
 Dip Time Sol (s), Clay Conc                                         &  68.92 \\
 Cure Time (min), Clay Conc                                          &  67.83 \\
 Cure Temp, Clay Conc                                                &  62.76 \\
 SG Coating, Clay Conc, pH Sol                                       &  82    \\
 Temp Alk Sol, Clay Conc, pH Sol                                     &  82    \\
 NaOH Wt\%, Clay Conc, pH Sol                                        &  82    \\
 Dip Time Alk (min), Clay Conc, pH Sol                               &  72.38 \\
 Hydro Time (h), Clay Conc, pH Sol                                   &  32.74 \\
 Dip Time Sol (s), Clay Conc, pH Sol                                 &  75.65 \\
 Cure Time (min), Clay Conc, pH Sol                                  &  70.52 \\
 Cure Temp, Clay Conc, pH Sol                                        &  71.84 \\
 Temp Alk Sol, Clay Conc, pH Sol, SG Coating                         &  87.46 \\
 NaOH Wt\%, Clay Conc, pH Sol, SG Coating                            &  87.46 \\
 Dip Time Alk (min), Clay Conc, pH Sol, SG Coating                   &  80.65 \\
 Hydro Time (h), Clay Conc, pH Sol, SG Coating                       &  43.08 \\
 Dip Time Sol (s), Clay Conc, pH Sol, SG Coating                     &  90.78 \\
 Cure Time (min), Clay Conc, pH Sol, SG Coating                      &  62.85 \\
 Cure Temp, Clay Conc, pH Sol, SG Coating                            &  58.38 \\
 Temp Alk Sol, Clay Conc, pH Sol, SG Coating, Dip Time Sol (s)       &  81.02 \\
 NaOH Wt\%, Clay Conc, pH Sol, SG Coating, Dip Time Sol (s)          &  81.02 \\
 Dip Time Alk (min), Clay Conc, pH Sol, SG Coating, Dip Time Sol (s) &  89.34 \\
 Hydro Time (h), Clay Conc, pH Sol, SG Coating, Dip Time Sol (s)     &  52.86 \\
 Cure Time (min), Clay Conc, pH Sol, SG Coating, Dip Time Sol (s)    &  73.46 \\
 Cure Temp, Clay Conc, pH Sol, SG Coating, Dip Time Sol (s)          &  67.5  \\
\hline
\end{tabular}
        \caption{Results of Forward Feature Selection for different features}
        \label{forward}
    \end{table*}
